Phylogenetics and the human microbiome.

### 2013-09-28 sbreview.tex
One... more... reference...

There are limitations to what we can learn using genetics because more intricate processes such as gene regulation may be at play, limiting what sequence-level phylogenetics can do.
Future work may move from more general ecological models to models that include specific interactions between microbes and the host \citep[e.g.][]{hooper2012interactions}.
MALDI-TOF is inexpensive, fast, and becoming accurate \citep{clark2013matrix}; it is thus likely to supplant 16S sequencing for routine identification of a single known microbe in culture.
However, for complex commmunity-level diagnoses sequencing and consequent analysis methods will still be required \citep[see review][]{Rogers2013271}.

>>>>

There are limitations to what we can learn using genetics because more intricate processes such as gene regulation may be at play, limiting what sequence-level phylogenetics can do.
Future work may move from more general ecological models to models that include specific interactions between microbes and the host \citep[e.g.][]{hooper2012interactions}.
MALDI-TOF is inexpensive, fast, and becoming accurate \citep{clark2013matrix}; it is thus likely to supplant 16S sequencing for routine identification of a single known microbe in culture.
However, for complex commmunity-level diagnoses sequencing and consequent analysis methods will still be required \citep[see review][]{Rogers2013271}, and inexpensive whole-genome sequencing will certainly have a profound impact on clinical practice \citep{didelot2012transforming}.
